An efficient acyclic contact planner for multiped robots

### 2016-01-20 body/equilibrium.tex
andrea sauf abstract
added missing figure on feasibility

According to Coulomb's law, the non slipping condition is verified if all the contact forces lie in the friction cone defined by the surface.
As classically done, we linearize the friction cone in a conservative fashion with a pyramid, described by four generating rays. We choose for instance:
\begin{equation*}
\mathbf{V}_{i} = \mat{\mathbf{n}_{i} + \mu \mathbf{t}_{i1} & \mathbf{n}_{i} -\mu \mathbf{t}_{i1} & \mathbf{n}_{i} + \mu \mathbf{t}_{i2} & \mathbf{n}_{i} - \mu \mathbf{t}_{i2}}^T
\end{equation*}

@@

In conclusion, the LP~\eqref{eq:dual} provides a method to assert rapidly static equilibrium, and returns a robustness value.
This robustness criterion can be immediately transformed into a heuristic, and eventually be ponderated with others.
Another option to enforce robustness is to set a minimum acceptable value for $b_0$, but as a result this conservative approach is not complete.

>>>>

According to Coulomb's law, the non slipping condition is verified if all the contact forces lie in the friction cone defined by the surface.
As classically done, we linearize the friction cone in a conservative fashion with a pyramid, described by four generating rays of unit length. We choose for instance:
\begin{equation*}
\mathbf{V}_{i} = \mat{\mathbf{n}_{i} + \mu \mathbf{t}_{i1} & \mathbf{n}_{i} -\mu \mathbf{t}_{i1} & \mathbf{n}_{i} + \mu \mathbf{t}_{i2} & \mathbf{n}_{i} - \mu \mathbf{t}_{i2}}^T
\end{equation*}

@@

In conclusion, the LP~\eqref{eq:dual} provides a method to assert rapidly static equilibrium, and returns a robustness value.
This robustness criterion can be immediately transformed into a heuristic, and eventually be pondered with others.
Another option to enforce robustness is to set a minimum acceptable value for $b_0$, but as a result this conservative approach is not complete.

### 2016-01-20 body/glossary.tex
added missing figure on feasibility

\newglossaryentry{ccequil}
{
  name=$C_{equil}$,
  description={Set of collision free full body configurations that are in static equilibrium}
}

\newglossaryentry{ccequil0}
{
  name=$C_{equil}^0$,
  description={Set of \textit{equilibrium feasible} root configurations $\mathbf{q}^{0}$, that verify $\exists \mathbf{q}^{\overline{0}},  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{equil}$}
}

>>>>

\newglossaryentry{ccequil}
{
  name=$C_{Equil}$,
  description={Set of collision free full body configurations that are in static equilibrium}
}

\newglossaryentry{ccequil0}
{
  name=$C_{Equil}^0$,
  description={Set of \textit{equilibrium feasible} root configurations $\mathbf{q}^{0}$, that verify $\exists \mathbf{q}^{\overline{0}},  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{Equil}$}
}

### 2016-01-20 body/overview.tex
added missing figure on feasibility

%~ \begin{table*}
%~ \centering
%~ \begin{tabular}{ c | >{\arraybackslash}m{200pt} | c}
   %~ Robot configuration set &  \centering Definition: $\mathbf{q} \in$ set $\Rightarrow$?  & Root configuration set\\
 %~ \hline
 %~ \hline
   %~ $C_{contact}$ & $\mathbf{q}$ collision free; at least one end effector in contact. &  $\mathbf{q}^{0} \in C_{contact}^0$ is ``contact feasible''.  \\
 %~ \hline
   %~ $C_{equil} \subset C_{contact} $ & $\mathbf{q}$  in static equilibrium &  $\mathbf{q}^{0} \in C_{equil}^0$ is ``equilibrium feasible''. \\
 %~ \end{tabular}
%~ \caption{TODO.}
%~ \label{tab:glossary}
%~ \quad
%~ \end{table*}

@@

\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a relevant guide path. The objective is to compute a path of root configurations that will allow contact creation. A desired requirement is to preserve the completeness of the planner: it should be able to explore any valid guide path, but at the same time, any computed guide path must lead to a sequence of contact configurations in static equilibrium.

More precisely, a root configuration is \gls{equilibrium feasible} if and only if there exists at least one joint configuration such that the robot satisfies two conditions:
\begin{description}
\item[C1]: is not in collision with the environment, 
%~ \item[C2] has at least one end-effector in contact with the environment, 
\item[C2]: is in static equilibrium. 
\end{description}
A requirement for C2 is the condition C3: at least one end-effector must be in contact with the environment.
C1 and C3 define \glslink{contact feasible}{\textit{contact feasibility}}, and can be efficiently approximated even without computing the contact points. C2 defines \glslink{equilibrium feasible}{\textit{equilibrium feasibility}}. C2 is difficult to approximate and requires the computation of the contact points, as well as the resolution of a linear program to compute the contact forces~\citep{Prete2016}.

@@

We define $C_{Contact}^0$ as the set of \gls{contact feasible} root configurations (that can satisfy C1 and C2).
Planning in $C_{Contact}^0$ boils down to planning in $\mathbb{R}^r$, which has an acceptable practical complexity.

An intuitive description of \gls{contact feasible} configurations is ``close, but not too close'': close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right leg in Figure~\ref{fig:contact_gen}--a); not too close, because the robot must avoid collision.
We approximate $C_{Contact}^0$ with a set $C_{reach}^0$, defined by the \textit{reachability condition}, a geometrical criterion based on this intuitive description.
Our objective is to find a root path such that the root (scaled by a factor $s>1$) is not in collision, while the reachable workspace is in collision with the environment.
In Section~\ref{rbprm} we detail how  $C_{reach}^0$ is designed and sampled to compute a guide path with a dedicated planner, the Reachability-Based RRT---RB-RRT--- (Figure~\ref{fig:framework}---\Pa).

@@

From a given start configuration, the planner proceeds in an iterative fashion along the discretized path: given a new root configuration, an inverse-kinematics solver 
is used to maintain the contacts that were previously existing. Possibly, some of these contacts cannot be maintained (because of joint limits or collisions).
Then the contacts are broken. Conversely, new contacts are created to ensure the static equilibrium of the robot.
The algorithm is designed so that only one contact can be created or broken between two successive configurations. This ensures that the interpolation between two configurations is achievable.
Details are presented in Section~\ref{sec:contact}.

>>>>

%~ \begin{table*}
%~ \centering
%~ \begin{tabular}{ c | >{\arraybackslash}m{200pt} | c}
   %~ Robot configuration set &  \centering Definition: $\mathbf{q} \in$ set $\Rightarrow$?  & Root configuration set\\
 %~ \hline
 %~ \hline
   %~ $C_{contact}$ & $\mathbf{q}$ collision free; at least one end effector in contact. &  $\mathbf{q}^{0} \in C_{contact}^0$ is ``contact feasible''.  \\
 %~ \hline
   %~ $C_{Equil} \subset C_{contact} $ & $\mathbf{q}$  in static equilibrium &  $\mathbf{q}^{0} \in C_{Equil}^0$ is ``equilibrium feasible''. \\
 %~ \end{tabular}
%~ \caption{TODO.}
%~ \label{tab:glossary}
%~ \quad
%~ \end{table*}

@@

\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a relevant guide path. The objective is to compute a path of root configurations that will allow contact creation. A desired requirement is to preserve the completeness of the planner: it should be able to explore any valid guide path, but at the same time, any computed guide path must lead to a sequence of contact configurations in static equilibrium.
The sets we introduce are illustrated in Figure~\ref{fig:dedefeas}.

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/2D_feas}
		\put (15,) {$C_{Equil}^0$      $\subset$} 
		\put (47,) {$C_{Contact}^0$ $\approx$ } 
		\put (76,) {$C_{Reach}^0$} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Illustration of several configurations sets used in this paper in a 2D scene. Obstacles are violet, and units are in meters. To show the sets in a 2D representation, all the rotational joints of HRP-2 are locked in the shown configuration, such that a torso configuration
is only described by two positional parameters (x and y). $C_{Equil}^0$ is included in $C_{Contact}^0$. $C_{Reach}^0$ approximates $C_{Contact}^0$. Depending on a parametrization, we can obtain $C_{Contact}^0 \subset C_{Reach}^0$. Considering the configurations around the top obstacle, we can observe a dramatic
divergence between  $C_{Equil}^0$  and $C_{Contact}^0$ when the problem is not \textit{\gls{cluttered}}.}
		   \label{fig:dedefeas}
\end{figure}

More precisely, a root configuration is \gls{equilibrium feasible} if and only if there exists at least one joint configuration such that the robot satisfies two conditions:
\begin{description}
\item[C1]: is not in collision with the environment, 
%~ \item[C2] has at least one end-effector in contact with the environment, 
\item[C2]: is in static equilibrium. 
\end{description}
A requirement for C2 is the condition C3: at least one end-effector must be in contact with the environment.
C1 and C3 define \glslink{contact feasible}{\textit{contact feasibility}}, and can be efficiently approximated even without computing the contact points. C2 defines \glslink{equilibrium feasible}{\textit{equilibrium feasibility}}, that we describe with the set $C_{Equil}^0$ (Figure~\ref{fig:dedefeas} -- Green). C2 is difficult to approximate and requires the computation of the contact points, as well as the resolution of a linear program to compute the contact forces~\citep{Prete2016}.

@@

We define $C_{Contact}^0$ (Figure~\ref{fig:dedefeas} -- Orange) as the set of \gls{contact feasible} root configurations (that can satisfy C1 and C2).
Planning in $C_{Contact}^0$ boils down to planning in $\mathbb{R}^r$, which has an acceptable practical complexity.

An intuitive description of \gls{contact feasible} configurations is ``close, but not too close'': close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right leg in Figure~\ref{fig:contact_gen}--a); not too close, because the robot must avoid collision.
We approximate $C_{Contact}^0$ with a set $C_{reach}^0$, defined by the \textit{reachability condition}, a geometrical criterion based on this intuitive description (Figure~\ref{fig:dedefeas} -- Red).
Our objective is to find a root path such that the root (scaled by a factor $s>1$) is not in collision, while the reachable workspace is in collision with the environment.
In Section~\ref{rbprm} we detail how  $C_{reach}^0$ is designed and sampled to compute a guide path with a dedicated planner, the Reachability-Based RRT---RB-RRT--- (Figure~\ref{fig:framework}---\Pa).

@@

From a given start configuration, the planner proceeds in an iterative fashion along the discretized path: given a new root configuration, an inverse-kinematics solver 
is used to maintain the contacts that were previously existing. Possibly, some of these contacts cannot be maintained (because of joint limits or collisions).
Then the contacts are broken. Conversely, new contacts are created to ensure the static equilibrium of the robot.
The algorithm is designed so that only one contact can be created or broken between two successive configurations. While does not provide guarantees that the interpolation between two configurations is achievable, it appears empirically as a reasonable heuristic.
Details are presented in Section~\ref{sec:contact}.

### 2016-01-20 body/rbprm.tex
complete, need abstract and section 4
added missing figure on feasibility

We consider the issue of computing a normalized guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow \mathbb{R}^r$ for the root of a multiped robot, connecting user-defined start and goal configurations (. As said in the previous section, the goal is to enforce that the guide can be discretized into a sequence of \gls{contact feasible} configurations. We denote by \gls{ccontact} the contact sub-manifold of the robot.

@@

However, between $W^0$ and $B^{Suf}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$.
%
We then consider the spaces $C_{s}^0$
 \begin{equation}
C^0_s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \text{ and } & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
If $s=1$, then $W^0_s$ = $W^0$, such that $C_1^0$ = $C_{Nec}$. We thus define $s \in \mathbb{R}^+$, since values inferior to $1$ can only introduce more errors.
The higher $s$, the closer this \gls{reachc} is to being sufficient, and if $s=1$, the search is complete (in the sense that all \gls{contact feasible} configurations can be found). The parametrization of $s$ defines a trade-off between these two desirable properties. $s$ can be chosen by hand, or automatically as explained in section TODO.
In the rest of the paper, we consider that an appropriate value $s^*$ of $s$ is chosen, and define \gls{creach0} $= C^0_{s^*}$.

>>>>

We consider the issue of computing a normalized guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow \mathbb{R}^r$ for the root of a multiped robot, connecting user-defined start and goal configurations. As said in the previous section, the goal is to enforce that the guide can be discretized into a sequence of \gls{contact feasible} configurations. We denote by \gls{ccontact} the contact sub-manifold of the robot.

@@

However, between $W^0$ and $B^{Suf}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$.
%
We then consider the spaces $C_{s}^0$
 \begin{equation}
C^0_s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \text{ and } & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
If $s=1$, then $W^0_s$ = $W^0$, such that $C_1^0$ = $C_{Nec}$. We thus define $s \in \mathbb{R}^+$, since values inferior to $1$ can only introduce more errors.
The higher $s$, the closer this \gls{reachc} is to being sufficient, and if $s=1$, the search is complete (in the sense that all \gls{contact feasible} configurations can be found). The parametrization of $s$ defines a trade-off between these two desirable properties. $s$ can be chosen by hand, or automatically as explained in Section~\ref{sec:params}.
In the rest of the paper, we consider that an appropriate value $s^*$ of $s$ is chosen, and define \gls{creach0} $= C^0_{s^*}$.

### 2016-01-20 body/results.tex
added missing figure on feasibility

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/car}
  \caption{
           Selected frames the car egress scenario. }
		   \label{fig:car}
\end{figure}

@@

\subsubsection{parametrization of the robustness equilibrium criterion} \label{sec:parrob}
Robustness is really important when considering practical applications on the robot, to account 
for the various uncertainties that result from environment and state estimator. However,
maximizing the robustness criterion is not necessarily optimal, because the resulting contacts will stay close to the center
of mass, thus not favoring the motion. In our experiments, we choose not to maximize the robustness,
but to empirically set a robustness treshold value under which a configuration is not considered to be in
static equilibrium (If no candidate reaches the treshold, instead of failing, the algorithm can eventually return the ``more robust'' configuration
found). Currently for HRP-2, a treshold value of 2 subjectively gives the best results in the considered scenarios, while 10 seems to be a good choice for HyQ. Both values do not
significantly slow down the planning times.

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation & Static equilibrium & Collision & Inverse Kinematics  & Total generation time & Time per step\\
 \hline
   Stairs (18) & 6 -- \textbf{13} --  24 & 13 --  \textbf{32} -- 329   & 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{14} \\
   Standing (24)& 4 -- \textbf{451} --  985 & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 310 --  \textbf{1622} -- 3429 & \textbf{66}  \\
   Car (61)& 1 -- \textbf{529} --  995 & 64 --  \textbf{85} -- 144   & 394 --  \textbf{735} -- 1422 & 3947 --  \textbf{13069} -- 36262 & 6775 --  \textbf{20890} -- 52963 & \textbf{342} \\
   Rubble (71)& 3 -- \textbf{524} --  993 & 242 --  \textbf{511} -- 3480   & 233 --  \textbf{505} -- 4564 & 180 --  \textbf{414} -- 3518 & 1400 --  \textbf{3058} -- 13126 & \textbf{43} \\
   Race (112)& 1 -- \textbf{501} --  995 & 266 --  \textbf{449} -- 3956   & 824 --  \textbf{1061} -- 2130 & 666 --  \textbf{874} -- 1613 & 2530 --  \textbf{3722} -- 10030 & \textbf{33}
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsubsection{Success rates}
We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoretical formulation. The extreme situation of the car egress scenario provides the less satisfying results in terms of kinematic failure. This is not
suprising considering the narrowness of the scene.
From a pragmatic point of view, regarding the computation times, we claim that our approach provides a satisfying compromise between completeness and efficiency.
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan a new contact sequence with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner for a given problem (our current implementation is single threaded) and to apply any successful result.

\begin{table*}
\centering
\begin{tabular}{ c | c | c | c | c }
 Scenario & Method  & Guide Path & Contact sequence & Interpolation \\
 \hline
   \multirow{3}{*}{Stair 20 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{5.42 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours} + \citeauthor{Carpentier2016}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & $ <$ 2s \\
 \hline
   \multirow{3}{*}{Stair 30 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{4.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & X \\
 \hline
   \multirow{3}{*}{Stair 40 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{10.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & \textbf{5 s} & \textbf{3 s} & X \\
 \hline
   \multirow{2}{*}{Table (car) egress} & \citeauthor{Bouyarmane2009, DBLP:conf/iser/EscandeKMG08} & 10 min & \multicolumn{2}{c}{3.5 hours}  \\
							 & \textbf{Ours}  & \textbf{529 ms} & \textbf{$<$ 21 s} & X \\
 \end{tabular}
\caption{TODO VERIFIE STATS A LA MAISON.}
\label{tab:compprev}
\quad
\end{table*}
\subsection{Comparison with previous work} \label{sec:compa}
Comparing our method with others is not trivial. Indeed, we focus on the contact planning aspect of the problem, and do not address
the interpolation in this paper, nor provide a strong guaranty that our sequence can be interpolated.
Papers in the state of the art, when they indicate the computation times, often only provide an overall computation
time, and we can not afford the important development resources required to reimplement them.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/car}
  \caption{
           Selected frames from the car egress scenario. }
		   \label{fig:car}
\end{figure}

@@

\subsubsection{parametrization of the robustness equilibrium criterion} \label{sec:parrob}
Robustness is really important when considering practical applications on the robot, to account 
for the various uncertainties that result from environment and state estimator. However,
maximizing the robustness criterion is not necessarily optimal, because the resulting contacts will stay close to the center
of mass, thus not favoring the motion. In our experiments, we choose not to maximize the robustness,
but to empirically set a robustness threshold value under which a configuration is not considered to be in
static equilibrium (If no candidate reaches the threshold, instead of failing, the algorithm can eventually return the ``more robust'' configuration
found). Currently for HRP-2, a threshold value of 2 subjectively gives the best results in the considered scenarios, while 10 seems to be a good choice for HyQ. Both values do not
significantly slow down the planning times.

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation (ms) & Static equilibrium (ms) & Collision (ms) & Inverse Kinematics (ms) & Total generation time (ms) & Time per step (ms)\\
 \hline
   Stairs (18) & 6 -- \textbf{13} --  24 & 13 --  \textbf{32} -- 329   & 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{14} \\
   Standing (24)& 4 -- \textbf{451} --  985 & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 310 --  \textbf{1622} -- 3429 & \textbf{66}  \\
   Car (61)& 1 -- \textbf{529} --  995 & 64 --  \textbf{85} -- 144   & 394 --  \textbf{735} -- 1422 & 3947 --  \textbf{13069} -- 36262 & 6775 --  \textbf{20890} -- 52963 & \textbf{342} \\
   Rubble (71)& 3 -- \textbf{524} --  993 & 242 --  \textbf{511} -- 3480   & 233 --  \textbf{505} -- 4564 & 180 --  \textbf{414} -- 3518 & 1400 --  \textbf{3058} -- 13126 & \textbf{43} \\
   Race (112)& 1 -- \textbf{501} --  995 & 266 --  \textbf{449} -- 3956   & 824 --  \textbf{1061} -- 2130 & 666 --  \textbf{874} -- 1613 & 2530 --  \textbf{3722} -- 10030 & \textbf{33}
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsubsection{Success rates}
We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoretical formulation. The extreme situation of the car egress scenario provides the less satisfying results in terms of kinematic failure. This is not
surprising considering the narrowness of the scene.
From a pragmatic point of view, regarding the computation times, we claim that our approach provides a satisfying compromise between completeness and efficiency.
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan a new contact sequence with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner for a given problem (our current implementation is single threaded) and to apply any successful result.

\begin{table*}
\centering
\begin{tabular}{ c | c | c | c | c }
 Scenario & Method  & Guide Path & Contact sequence & Interpolation \\
 \hline
   \multirow{3}{*}{Stair 20 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{5.42 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours} + \citeauthor{Carpentier2016}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & $ <$ 2s \\
 \hline
   \multirow{3}{*}{Stair 30 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{4.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & X \\
 \hline
   \multirow{3}{*}{Stair 40 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{10.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & \textbf{5 s} & \textbf{3 s} & X \\
 \hline
   \multirow{2}{*}{Table (car) egress} & \citeauthor{Bouyarmane2009, DBLP:conf/iser/EscandeKMG08} & 10 min & \multicolumn{2}{c}{3.5 hours}  \\
							 & \textbf{Ours}  & \textbf{529 ms} & \textbf{$<$ 21 s} & X \\
 \end{tabular}
\caption{TODO VERIFIE STATS A LA MAISON.}
\label{tab:compprev}
\quad
\end{table*}
\subsection{Comparison with previous work} \label{sec:compa}
Comparing our method with others is not trivial. Indeed, we focus on the contact planning aspect of the problem, and do not address
the interpolation in this paper, nor provide a strong guarantee that our sequence can be interpolated.
Papers in the state of the art, when they indicate the computation times, often only provide an overall computation
time, and we can not afford the important development resources required to reimplement them.
